Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2021-02-08 paper/paper.Rmd
Adding results

defined on $\{y : y>0$ and $1 + \xi y/\tilde{\sigma}\}$, where
$$\tilde{\sigma} = \sigma + \xi(x - \mu)$$
An approximation between the GEV and GP distributions occurs where the values over a threshold excess (location, $\mu$) have a corresponding approximate GP distribution [@coles2001introduction]. The parameters in the GP distribution of threshold excesses are determined by the values in the corresponding GEV distribution of a random variable $X$ (scale $\sigma$, location $\mu$). In both distributions, the shape parameter $\xi$ is dominant to determine the tail of the distribution. In the generalized Pareto distribution, a shape parameter $\xi<0$ the tail has an upper bound at $\mu - \tilde{\sigma}/\xi$ following a Beta distribution function;whereas a shape parameter $\xi>0$ follows a heavy tail with no upper limit. In the special case of $\xi = 0$, the GP distribution function approximates to an exponential distribution with a parameter of $1/\tilde{\sigma}$ (Figure 3b.) [@coles2001introduction].

Our study focused on long-distance dispersal events defined as any dispersal event over 500m from the parent tree in order to compare our results to previous studies in this same ecological system [@holbrook_dispersal_2009; @holbrook_home_2011; @holbrook_using_2007]. However, when selecting a threshold for a POT approach, it is also possible to use diagnostic plots by fitting the data to a sequence of thresholds, with the goal of finding the lowest threshold that provides similar parameter values to any other higher threshold. We performed these analysis and we report our parameter estimates and expected probability of occurrence of long-distance events using the thresholds from diagnostics plots. We fit Generalized Pareto distributions to the data via maximum likelihood using the package extRemes [@extRemes2] in R [@Rcit].

@@

>>>>

defined on $\{y : y>0$ and $1 + \xi y/\tilde{\sigma}\}$, where
$$\tilde{\sigma} = \sigma + \xi(x - \mu)$$
An approximation between the GEV and GP distributions occurs where the values over a threshold excess (location, $\mu$) have a corresponding approximate GP distribution [@coles2001introduction]. The parameters in the GP distribution of threshold excesses are determined by the values in the corresponding GEV distribution of a random variable $X$ (scale $\sigma$, location $\mu$). In both distributions, the shape parameter $\xi$ is dominant to determine the tail of the distribution. In the generalized Pareto distribution, a shape parameter $\xi<0$ the tail has an upper bound at $\mu - \tilde{\sigma}/\xi$ following a Beta distribution function, whereas a shape parameter $\xi>0$ follows a heavy tail with no upper limit. In the special case of $\xi = 0$, the GP distribution function approximates to an exponential distribution with a parameter of $1/\tilde{\sigma}$ (Figure 3b.) [@coles2001introduction]. The focus on these shape parameters, both in the case of the Generalized Pareto and the Weibull distribution, is due to the interest in long-distance dispersal events, and using these parameters as a comparisson between dispersal kernels allows us to compare which kernels have higher probabilities for long-distance dispersal events.

Initially, we defined long-distance dispersal events defined as any dispersal event over 500m from the parent tree in order to compare our results to previous studies in this same ecological system [@holbrook_dispersal_2009; @holbrook_home_2011; @holbrook_using_2007]. We used this threshold to assess the percentage of LDD events reported in table 1. However, when selecting a threshold for a POT approach, using a generalized Pareto distribution, we can use diagnostic plots by fitting the data to a sequence of thresholds, with the goal of finding the lowest threshold that provides similar parameter values to any other higher threshold. We performed these analysis and we report our parameter estimates for the generalized Pareto and expected conditional probabilities of long-distance dispersal events using the thresholds from diagnostics plots. We fit Generalized Pareto distributions to the data via maximum likelihood using the package extRemes [@extRemes2] in R [@Rcit].

@@

## Simulation of seed dispersal distances under the three movement models
We generated seed dispersal distances from combining animal movement and seed gut retention time. The three models we used to simulate the dispersal distances differ in their approach to characterize variation between the animals dispersing seeds. In the case of our null model, where each animal's step length is sampled from an exponential distribution with the same rate parameter, we would expect to find no differences between the dispersal kernels generated by each of the animals. On the contrary, for the case of simulation models that include individual and family level variation in animal movement, we expected the seed dispersal kernels generated by each individual to show variation. Indeed, Figure 4A shows that individual and family level simulation models show different seed dispersal kernels for each individual bird, whereas in the null model, individual seed dispersal kernels actually overlap with the average dispersal kernel (black line). We generated the average seed dispersal kernels (black lines in Figure 4A) for each of the simulation models by taking all of the seed dispersal distances from the simulation. We did this as in the field we can perform maternity analysis to know seed origin, but it is more complicated to know which specific animal dispersed each seed. Therefore, the average seed dispersal kernels would better reflect the type of data we would collect from field surveys of seed dispersal. From now on, we refer to each of these average seed dispersal kernels as the kernel generated by each of the three simulation models: null kernel, individual kernel, and family kernel.
